Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance

### 2019-06-04 Manuscript/manuscript.Rmd
Remove hardcoded path

![**Model Construction.** An illustration of the proposed model construction given cell line specific Hi-C data. Above is an example of a subsection of the contact matrix for chromosome 14 (at megabase scale) on GM12878 [@durand2016juicer]. The contact matrix is a visualization of the interconnectivity of the linear genome at 100 kb resolution. The boundary coordinates of TADs were identified using the Arrowhead algorithm. To account for the uncertainty in TAD boundary detection, each boundary point was flanked on both sides by resolution-specific genomic regions (bins). The response vector $Y$, used for classification, was determined by whether a genomic bin overlapped with a flanked boundary region ($Y=1$) or not ($Y=0$). The spatial relationship between positional coordinates of various functional genomic annotations, obtained from the UCSC Genome Browser Database, together with the genomic bins were then used to define the feature space of the models represented by the data matrix $\textbf{X} = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure1_model_construction_V3.png)

>>>>

![**Model Construction.** An illustration of the proposed model construction given cell line specific Hi-C data. Above is an example of a subsection of the contact matrix for chromosome 14 (at megabase scale) on GM12878 [@durand2016juicer]. The contact matrix is a visualization of the interconnectivity of the linear genome at 100 kb resolution. The boundary coordinates of TADs were identified using the Arrowhead algorithm. To account for the uncertainty in TAD boundary detection, each boundary point was flanked on both sides by resolution-specific genomic regions (bins). The response vector $Y$, used for classification, was determined by whether a genomic bin overlapped with a flanked boundary region ($Y=1$) or not ($Y=0$). The spatial relationship between positional coordinates of various functional genomic annotations, obtained from the UCSC Genome Browser Database, together with the genomic bins were then used to define the feature space of the models represented by the data matrix $\textbf{X} = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.](Figures/figure1_model_construction_V3.png)
